intro

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted comment

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. <!-- Der letzte Teil des Satzes klingt komisch, weiß aber nicht so richtig, was ihr sagen wollt.-->
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
People choose a strategy that they prefer for different, relatively well-known reasons. <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->
However, nothing is revealed about the strategy that is *not chosen*.

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached. <!-- Hier komme ich noch nicht so ganz mit, könntet ihr das noch klarer beschreiben, was hier passiert? Meint ihr folgendes?: ... The lower monetary value is assigned to different options? oder The lower monetary value is further lowered? Also wird geschaut, wie tief der Wert sein muss, damit die andere Strategie gewählt wird? Sorry, obwohl ihr es schon so oft erklärt habt, bin ich hier immer noch lost, aber das könnte ja anderen Reviewers auch so gehen. Und das die Revs genau in Westbrook schauen, das könnt ihr leider nicht erwarten. -->
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
<!-- Figure 1 macht das Paradigma schon deutlicher, aber alles verstehe ich noch nicht, z.B. es könnte deutlicher werden, dass der monetäre Wert für die gewählte Strategie sich über die mehreren durchläufe ergibt (übrigens sprecht ihr manchmal von € manchmal von $ das sollte einheitlich sein). Und was ich leider gar nicht verstehe, ist wie sich immer der Wert 1 für die am Ende preferierte Strategie ergibt (also z.B. in der oberen Hälfte SV StrategyB(Strategy A) = 1)-->
```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm."}
include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
```

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological arousal (EMG). <!-- Denise: "or/and physiological valence" see comment below --> Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological arousal as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->

>>>>

How do people choose strategies from their repertoire? 
Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. <!-- Der letzte Teil des Satzes klingt komisch, weiß aber nicht so richtig, was ihr sagen wollt.-->
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards, they choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
People choose a strategy that they prefer for different, relatively well-known reasons[@Sheppes2014]. <!-- Denise: Ist das so? Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason? Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert. Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde. Und das ihr deshalb nun so vorgeht? -->
However, nothing is revealed about the strategy that is *not chosen*.

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached. <!-- Hier komme ich noch nicht so ganz mit, könntet ihr das noch klarer beschreiben, was hier passiert? Meint ihr folgendes?: ... The lower monetary value is assigned to different options? oder The lower monetary value is further lowered? Also wird geschaut, wie tief der Wert sein muss, damit die andere Strategie gewählt wird? Sorry, obwohl ihr es schon so oft erklärt habt, bin ich hier immer noch lost, aber das könnte ja anderen Reviewers auch so gehen. Und das die Revs genau in Westbrook schauen, das könnt ihr leider nicht erwarten. -->
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).

```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can be represented by our paradigm."}
include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
```

The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort. 
The following hypotheses are proposed:
<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen. Z.B.: Warum wird Corrugator und Levator untersucht? m.E. müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal? Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen. oder steht corrugator für arousal und levator für valence? dann auch so benennen. Außerdem subjective arousal/ subjective effort auch immer konsistent benennen. Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
